---
title: "STAT345 Midterm"
author: "Tarren Nimmow"
date: "2023-03-28"
output:
  word_document: default
---

```{r setup, echo=FALSE, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE, results='hide', message=FALSE}
library(nbastatR)
library(tidyverse)
library(ggplot2)
library(ggforce)
library(gganimate)
library(ggtext)
library(png)
library(grid)
library(jpeg)
img <- readJPEG("output-onlinejpgtools.jpg")
```

```{r, echo=FALSE, results='hide'}
# This code chunk creates a new dataset of some bucks shooting stats from 2013-2021
Sys.setenv(VROOM_CONNECTION_SIZE=500072)

bucks_shots <- teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2013, nest_data = F, return_message = T) %>%
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2014, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2015, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2016, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2017, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2018, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2019, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2020, nest_data = F, return_message = T)) %>% 
bind_rows(teams_shots(teams = "Milwaukee Bucks", season_types = "Regular Season", seasons = 2021, nest_data = F, return_message = T)) 

bucks_shots <- select(bucks_shots, "namePlayer","yearSeason", "typeShot", "locationX", "locationY", "isShotMade", "yearSeason")
```

```{r, echo=FALSE, warning=FALSE}
# This code creates a chart of every shot taken in a bucks season from 2014-2021
ggplot(bucks_shots, aes(locationX, locationY, color = isShotMade, shape = typeShot)) +
  theme(panel.background = element_rect(fill = "transparent", color = NA)) +
  annotation_custom(rasterGrob(img), xmin=-252, xmax=252, ymin=-47.5, ymax=893) +
  geom_point(mapping = aes(x=locationX, y=locationY), alpha = 0.5, size = .75) +
  scale_color_manual(name = "Made/Missed", values= c("red", "green"), labels = c("Missed", "Made")) +
  scale_shape_manual(name = "Shot Type", values = c(0,2), labels = c("2PT", "3PT")) +
  ggtitle("Every Bucks Shot by Season") +
  xlab("Baseline") +
  ylab("Sideline") +
  coord_fixed() +
  transition_time(yearSeason) +
  ease_aes('linear') +
  labs(subtitle = 'Year: {closest_state}') +
  theme(legend.text = element_text(size=12)) + 
  theme(legend.key.size = unit(2, "lines")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank()) +
  transition_states(yearSeason, transition_length = 2, state_length = 10) +
  ease_aes('linear')
```

The graphic shows every season’s shot attempts from 2013-2021
It displays where the shot was taken from (location)
It displays whether or not the shot was made (color)
It displays the type of field goal attempted (shape)


More detailed version
The graphic shows every season's shot attempts from 2012-2021
It displays where the shot was taken from (location)
It displays whether or not the shot was made by the color of the point
Cream: Shot was missed
Green: Shot was made
It displays the type of field goal attempted by shape
Square: 2PT attempt
Triangle: 3PT attempt



2013

Total Shots Attempted: 7196

Total 3s Attempted: 1669

Total 3s Made: 601

3pt%: 36%

Total 2s Attempted: 5527

Total 2s Made: 2527

2pt%: 45.7%



2014

Total Shots Attempted: 6735

Total 3s Attempted: 1551

Total 3s Made: 548

3pt%: 35.3%

Total 2s Attempted: 5184

Total 2s Made: 2404

2pt%: 46.3%



2015

Total Shots Attempted: 6722

Total 3s Attempted: 1500

Total 3s Made: 545

3pt%: 36.3%

Total 2s Attempted: 5222

Total 2s Made: 2538

2pt%: 48.6%



2016

Total Shots Attempted: 6726

Total 3s Attempted: 1263

Total 3s Made: 437

3pt%: 34.6%

Total 2s Attempted: 5463

Total 2s Made: 2705

2pt%: 49.5%



2017

Total Shots Attempted: 6701

Total 3s Attempted: 1932

Total 3s Made: 713

3pt%: 36.9%

Total 2s Attempted: 4769

Total 2s Made: 2462

2pt%: 51.6%



2018

Total Shots Attempted: 6807

Total 3s Attempted: 2024

Total 3s Made: 718

3pt%: 35.5%

Total 2s Attempted: 4783

Total 2s Made: 2539

2pt%: 53.1%



2019

Total Shots Attempted: 7471

Total 3s Attempted: 3134

Total 3s Made: 1105

3pt%: 35.3%

Total 2s Attempted: 4337

Total 2s Made: 2450

2pt%: 56.5%



2020

Total Shots Attempted: 6638

Total 3s Attempted: 2840

Total 3s Made: 1007

3pt%: 35.5%

Total 2s Attempted: 3798

Total 2s Made: 2153

2pt%: 56.7%



2021

Total Shots Attempted: 6610

Total 3s Attempted: 2669

Total 3s Made: 1038

3pt%: 38.9%

Total 2s Attempted: 3941

Total 2s Made: 2183

2pt%: 55.4


```{r, echo=FALSE}
# This creates plots of every shot Khris Middleton took in every season from 2014-2021
ggplot(data = filter(bucks_shots, namePlayer == "Khris Middleton")) +
  theme(panel.background = element_rect(fill = "transparent", color = NA)) +
  annotation_custom(rasterGrob(img), xmin=-250, xmax=250, ymin=-47.5, ymax=892.5) +
  geom_point(mapping = aes(x = locationX, y = locationY, color = isShotMade, shape = typeShot)) +
  scale_color_manual(name = "Made/Missed", values= c("red", "green"), labels = c("Missed", "Made")) +
  scale_shape_manual(values = c("2PT Field Goal" = 1, "3PT Field Goal" = 2)) +
  labs(title = "Khris Middleton Shot Chart (Regular Season)", x = "X-Coordinate", y = "Y-Coordinate", color = "Made Shot", shape = "Type of Shot", subtitle = 'Year: {closest_state}') +
  coord_fixed() +
  transition_states(yearSeason, transition_length = 2, state_length = 5) +
  ease_aes('linear') +
  theme_void()
```

2014 Khris Middleton

Total Shots Attempted: 854

Total 3s Attempted: 290

Total 3s Made: 120

3pt%: 41.4%

Total 2s Attempted: 564

Total 2s Made: 256

2pt%: 45.4%



2015 Khris Middleton

Total Shots Attempted: 869

Total 3s Attempted: 268

Total 3s Made: 109

3pt%: 40.7%

Total 2s Attempted: 601

Total 2s Made: 297

2pt%: 49.4%



2016 Khris Middleton

Total Shots Attempted: 1142

Total 3s Attempted: 361

Total 3s Made: 143

3pt%: 39.6%

Total 2s Attempted: 781

Total 2s Made: 364

2pt%: 46.6%



2017 Khris Middleton

Total Shots Attempted: 333

Total 3s Attempted: 104

Total 3s Made: 42.3%

3pt%: 

Total 2s Attempted: 229

Total 2s Made: 105

2pt%: 45.9%



2018 Khris Middleton

Total Shots Attempted: 1272

Total 3s Attempted: 407

Total 3s Made: 146

3pt%: 35.9%

Total 2s Attempted: 865

Total 2s Made: 447

2pt%: 51.7%



2019 Khris Middleton

Total Shots Attempted: 1148

Total 3s Attempted: 474

Total 3s Made: 179

3pt%: 37.8%

Total 2s Attempted: 674

Total 2s Made: 327

2pt%: 48.5%



2020 Khris Middleton

Total Shots Attempted: 947

Total 3s Attempted: 354

Total 3s Made: 147

3pt%: 41.5%

Total 2s Attempted: 593

Total 2s Made: 324

2pt%: 54.6%



2021 Khris Middleton

Total Shots Attempted: 1074

Total 3s Attempted: 365

Total 3s Made: 151

3pt%: 41.4%

Total 2s Attempted: 709

Total 2s Made: 360

2pt%: 349

```{r, echo=FALSE}
# This creates plots of every shot Giannis Antetokounmpo took in every season from 2014-2021
ggplot(data = filter(bucks_shots, namePlayer == "Giannis Antetokounmpo")) +
  theme(panel.background = element_rect(fill = "transparent", color = NA)) +
  annotation_custom(rasterGrob(img), xmin=-250, xmax=250, ymin=-47.5, ymax=892.5) +
  geom_point(mapping = aes(x = locationX, y = locationY, color = isShotMade, shape = typeShot)) +
  scale_color_manual(name = "Made/Missed", values= c("red", "green"), labels = c("Missed", "Made")) +
  scale_shape_manual(values = c("2PT Field Goal" = 1, "3PT Field Goal" = 2)) +
  labs(title = "Giannis Antetokounmpo Shot Chart (Regular Season)", x = "X-Coordinate", y = "Y-Coordinate", color = "Made Shot", shape = "Type of Shot", subtitle = 'Year: {closest_state}') +
  coord_fixed() +
  transition_states(yearSeason, transition_length = 2, state_length = 5) +
  ease_aes('linear') +
  theme_void()
```


2014 Giannis Antetokounmpo 

Total Shots Attempted: 418 

Total 3s Attempted: 118 

Total 3s Made: 41 

3pt%: 34.7% 

Total 2s Attempted: 300 

Total 2s Made: 132 

2pt%: 44.0%") 



2015 Giannis Antetokounmpo

Total Shots Attempted: 780

Total 3s Attempted: 44

Total 3s Made: 7

3pt%: 15.9%

Total 2s Attempted: 736

Total 2s Made: 376

2pt%: 51.1%



2016 Giannis Antetokounmpo

Total Shots Attempted: 1011

Total 3s Attempted: 107

Total 3s Made: 27

3pt%: 25.2

Total 2s Attempted: 904

Total 2s Made: 485

2pt%: 53.7%



2017 Giannis Antetokounmpo

Total Shots Attempted: 1258

Total 3s Attempted: 179

Total 3s Made: 49

3pt%: 27.4%

Total 2s Attempted: 1079

Total 2s Made: 607

2pt%: 56.3%



2018 Giannis Antetokounmpo

Total Shots Attempted: 1672

Total 3s Attempted: 410

Total 3s Made: 43

3pt%: 30.7%

Total 2s Attempted: 1262

Total 2s Made: 699

2pt%: 55.4%



2019 Giannis Antetokounmpo1195

Total Shots Attempted: 

Total 3s Attempted: 151

Total 3s Made: 52

3pt%: 25.6%

Total 2s Attempted: 1044

Total 2s Made: 669

2pt%: 64.1%



2020 Giannis Antetokounmpo

Total Shots Attempted: 1238

Total 3s Attempted: 293

Total 3s Made: 89

3pt%: 30.4%

Total 2s Attempted: 945

Total 2s Made: 596

2pt%: 63.1%



2021 Giannis Antetokounmpo

Total Shots Attempted: 1121

Total 3s Attempted: 224

Total 3s Made: 67

3pt%: 29.9%

Total 2s Attempted: 897

Total 2s Made: 559

2pt%: 63.4%